PCoA with bray curtis on KO abundance

### 2019-11-03 scripts/13_PCoA_brayCurtis_KO_abundance.Rmd
the tox are not separating the sample at all for spp table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
library(tidyverse)
library(vegan)
```

@@

bc_dist <-  vegdist(t(spp), "bray")
pc_bc <- cmdscale(bc_dist, k = 2) 
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$tox_col, main = 'species abundance color by tox')
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$CR_col, main = 'species abundance color by CR')
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)  
library(tidyverse)
library(ggpubr)
library(vegan)
```

@@

bc_dist <-  vegdist(t(spp), "bray")
pc_bc <- cmdscale(bc_dist, k = 2) 
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$tox_col, main = 'species abundance color by tox')
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$CR_col, main = 'species abundance color by CR')

# updated pheno
uppheno <- read_csv('../data/cleaned_pheno/pheno_w_expanded_tox.csv', col_types = 'cfffffff')

# ggplot 
pc_bc %>% 
  as.data.frame() %>% 
  rownames_to_column('Sampleid') %>% 
  full_join(uppheno, by = 'Sampleid') %>% 
  ggdotplot(x  = 'V1', y = 'V2', color =  'Toxicity', fill = 'Toxicity', 
            palette = 'lancet')
